Self Regulation Ontology Retest Data Report

### 2017-11-10 code/SRO_Report.Rmd
jdm poster

retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]

@@

Comparison of survey measures to cognitive task measures in the bootstrapped results. Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure. (Same result as seen in point estimates comparison).

@@

summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
```

Checking DDM results in the bootstrapped estimates. Same as before too.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
  mutate(label_1 = trim(label_1),
         label_2=trim(label_2),
         label_3=trim(label_3))%>%
  filter(ddm_task == 1) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')
```

```{r}
summary(lmerTest::lmer(icc ~ label_1 + (1|dv) ,tmp))
```

```{r}
summary(lmerTest::lmer(icc ~ label_3 + (1|dv) ,tmp))
```

```{r warning=FALSE, message=FALSE}
poster_vars <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/poster_var_list.csv', header=F)

names(poster_vars) = "var"

boot_df_poster = boot_df[boot_df$dv %in% poster_vars$var,]

boot_df_poster = boot_df_poster%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  arrange(task_group, var)

boot_df_poster = boot_df_poster %>%
  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
  rename(icc = icc.x, point_est = icc.y)

#Manual correction
boot_df_poster = boot_df_poster %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", task)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group))
```

```{r warning=FALSE, message=FALSE} 
p4 <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#00BFC4')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p5 <- boot_df_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#F8766D')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot.jpg')
```

```{r echo=FALSE}
rm(p4, p5, p6)
```

```{r}
p4_t <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p5_t <- boot_df_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

>>>>

# retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]

@@

Comparison of survey measures to cognitive task measures in the bootstrapped results. Multilevel model with random intercepts for each measure and fixed effect of survey versus cognitive measure.

@@

boot_df %>%
  group_by(task) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r}
summary(lmerTest::lmer(icc ~  task + (1|dv), boot_df))
```

```{r warning=FALSE, message=FALSE}
boot_df %>%
  ggplot(aes(icc, fill = task))+
  geom_histogram(alpha=0.5, position='identity')+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC")
```

Checking DDM results in the bootstrapped estimates. Variables using all trials are significantly more reliable compared to difference scores. Raw measures don't differ from DDM parameters. Which DDM is better depends on whether all trials are used.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition") %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp %>%
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r}
summary(lmerTest::lmer(icc ~ overall_difference*raw_fit + (1|dv) ,tmp))
```

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank())

ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 20, height = 8, units = "in", limitsize = FALSE)
```

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp = tmp %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  arrange(task_group, var)

tmp = tmp %>%
  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
  rename(icc = icc.x, point_est = icc.y)

#Manual correction
tmp = tmp %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group))
```

Variable level summary of bootstrapped reliabilities.

```{r warning=FALSE, message=FALSE} 
p4 <- tmp %>%
  filter(task == 'task',
         raw_fit == 'raw') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#00BFC4')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p5 <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#F8766D')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

ggsave('Bootstrap_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)

rm(p4, p5, p6)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Var_Plot.jpg')
```

```{r message=FALSE, warning=FALSE}
p4_t <- tmp %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()
